Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-02 src/paper.tex
update

\section{Introduction}
Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers.
In real life, speech signals are usually companied with background noise or other speakers' speeches. 
Our humans might grasp the speech but machine is not the case.
These signals may not be optimal for tasks like speaker verification. 
Target speaker extraction is a sub-task of speech separation.

>>>>

\section{Introduction}
Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers. This task is easy for humans but not for computers. 
In real life, speech signals are usually companied with background noise or other speakers' speeches. 
These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of this task.

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. The separation
